Placeholder Title... Something About Delegating Quantum Computations

### 2019-11-13 longoutput.tex
Change wording
Fix confusing notation
Add TODO on using Mahadev's scheme
Fix wording

In the case for decision problems, amplifying the gap between acceptance and rejection probabilities is trivial. As seen in \cite{kitaev2002classical}, a prover, honest or not, cannot do better than sending $n$ identical copies of some state. As a result, a simple Chernoff bound would suffice. The same reasoning does not generalize to our case, so instead we give the following proof.

Suppose $\mathcal{F}$ accepts $\ket{\psi}$ with probability $\frac{1}{2}$, and any states perpendicular to it with probability $\frac{1}{2}-\Delta$. We start by considering simpler inputs before moving to the general case.

@@

\begin{observation}
	If the input is of the form $\ket{\phi^{\otimes n+m}}$, \autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers.
\end{observation}

\begin{theorem}
	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, its output when accepted has $\frac{p}{\delta}$ to be rejected by $\mathcal{F}$.
\end{theorem}
\begin{proof}
	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.

@@

	Let $J=\set{j:\mathcal{F}(\ket{\rho_j})<\frac{1}{2}-\varepsilon}$.

	$\Rightarrow\forall j\in J$, $q_j<p$.

@@

>>>>

In the case for decision problems, amplifying the gap between acceptance and rejection probabilities is trivial. As seen in \cite{kitaev2002classical}, a prover, honest or not, cannot do better than sending $n$ identical copies of some state. As a result, a simple Chernoff bound would suffice. The same reasoning does not generalize to our case, so instead we give the following proof. We start by considering simpler inputs before moving on to the general case.

Suppose $\mathcal{F}$ accepts $\ket{\psi}$ with probability $\frac{1}{2}$, and any states perpendicular to it with probability $\frac{1}{2}-\Delta$.

@@

\begin{observation}
	\autoref{AlgAmp1} applies a Chernoff bound to the first $n$ registers
\end{observation}

\begin{theorem}
	When \autoref{AlgAmp1} accepts an input with probability greater than $\delta$, conditioned on this acceptance, $\mathcal{F}$ has probability at least $1-\frac{p}{\delta}$ to accept each register of the output.
\end{theorem}
\begin{proof}
	Note that the input is a classical probability distribution over inputs $\ket{\rho_i^{\otimes n+m}}$ with $w_i$ as weights.

@@

	Let $J=\set{j:q_j<p}$.

@@

\Ethan{Now use \cite{mahadev_delegation} to turn this into a server-client thing}
